\Large{Holier Than Thou: Partisan Gap in Consumption\\ of Pornography Online}\footnote{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}}

### 2022-12-20 ms/adult.tex
Update quantile regressions
Updating quantile regressions using the new data removing obvious false positives of porn sites.

The consumption of pornography is concentrated. Traffic to the top 10 most frequented porn sites ten times that of traffic to all other porn sites outside the top 10 (approximately 120 minutes vs 12 minutes, see \crefrange{fig:concentration_porn_consumption}{fig:concentration_porn_consumption_by_party}). 
For panelists who consume porn, close to 80 percent of their traffic to adult sites is concentrated in just one porn site (\cref{fig:concentration_porn_consumption_topX_by_party}). This behavior does not differ substantially party.

>>>>

The consumption of pornography is concentrated. Traffic to the top 10 most frequented porn sites more than 12 times that of traffic to all other porn sites outside the top 10 (approximately 109 minutes vs 9 minutes, see \crefrange{fig:concentration_porn_consumption}{fig:concentration_porn_consumption_by_party}). 
For panelists who consume porn, close to 80 percent of their traffic to adult sites is concentrated in just one porn site (\cref{fig:concentration_porn_consumption_topX_by_party}). This behavior does not differ substantially party.
